Consistency scores in text data

### 2020-07-28 outputs/documents/paper.Rmd
Revisited and add to the section of GPT-2. Add literatures on GloVe, Word2Vec and BERT

### Article: Class-Based n-gram Models of Natural Language (1992)
Syntax-based (grammartical) and semantic-based (sensible) word classifications in n-gram models.

### Article: A Statistical Approach to Automatic OCR Error Correction in Context (1996)
Context-sensitive correction system to both non-word and real-word errors based on n-gram models applied to OCR postprocessing.

## Pre-trained language models

@@

In recent years, the use of pre-trained language models has played a significant role in advancing natural language processing (NLP) tasks such as reading comprehension, text generation, and even creative writing **(Ke-Li add ref)**. Pre-trained models remove the need for researchers to prepare training datasets or allot computational resources to the stage of pre-training. Because of this, there has been substantial development in NLP research.

OpenAI's GPT-3 is a generative, pre-trained, task-agnostic, language model that was announced by OpenAI in June 2020 **(Ke-Li add ref)**. OpenAI is an AI research company who openly pursues Artificial General Intelligence—to have machines learn and understand any intellectual tasks as human do **(Ke-Li add ref)**. GPT-3 is the third Generative Pre-trained Transformer language model publicly released by OpenAI. It has '175 billion parameters' and can learn NLP tasks with just a few examples. OpenAI claims that the text generation by GPT-3 is 'difficult for humans to distinguish from authentic human content' (@brown2020language). Since the API of GPT-3 at the moment is only available to a few invited users, public applications of GPT-3 are limited. On the other hand, its predecessor, GPT-2, has enabled researchers made breakthroughs in the past years. @alt2019fine extended GPT-2 to relation extraction, which is a task of identifying the relationship between concepts appeared in text. They had shown a milestone in predicting larger range of distinct relation types with higher confidence **(Ke-Li add ref)**. In the field of speech recognition, data scarcity is often an issue due to the difficulty to collect large amount of data from human for learning **(Ke-Li add ref)**. @bird2020lstm employed GPT-2 as part of the solution to generate augmented data for classification. GPT-2 also helped NLP researchers tackling the task of textual paraphrasing **(Ke-Li add ref)**. @hegde2020unsupervised used GPT-2 to build an unsupervised paraphrasing model that is not restricted by domain shift within an article, which is a problem faced by the usual supervised models of paraphrasing.  
**(Ke-Li please find papers that use it, describe them, and add refs - look on arXiv)**.

GPT-3 is a Transformer-based model that has over 175 billions of parameters (@brown2020language). Proposed by @vaswani2017attention, the Transformer is a novel network architecture that outperforms RNN-based models in computational efficiency **(Keli add citation)**. The parameters refer to the weights of the connections that enable the neural network to learn **(Keli add citation)**. In the past few years, the growth of parameters of transformer language models expands rapidly. The first generation GPT has 110 million parameters. Released in 2018, GPT-2 has 1.6 billion parameters, and within two years, GPT-3 has grown the size to 175 billion, which is over 100 times than its predecessor . The more parameters there are the better the model can generalize to new tasks; therefore, the increasing amount of parameters accelerates the improvements in text synthesis and downstream NLP tasks **(Keli add citation)**. GPT-3 can learn NLP tasks with just a handful of example; OpenAI refers this ability as few-shot learning, or in-context learning. Few-shot learning means that the model  **(Keli add citation)**. 
As a result, we only need to provide GPT-3 a few demonstrations for it to learn a new NLP task. **(Ke-Li add more detail about what it needs and what it outputs and how it works).**. For example, OpenAI team trained GPT-3 to generate "news articles". The prompt input is a plausible first sentence of a news story written by human, and the output is an entire news article generated by the model itself. Without the demonstrations, GPT-3 tends to treat the prompts as "tweets" and generate texts that serve as responses or follow-up tweets. The team fed a few previous news articles in the model’s context as demonstrations, and the model learned to produce the outputs that adapt to the style and length of news stories (@brown2020language). This few-shot learning ability indicates that the model can learn like human do and would democratize the use of language models to broader fields. **(Ke-Li please find the language that they use for this and then we need to make ours consistent with theirs).**

>>>>

## Word Embedding Models: GloVe and Word2Vec

**Article: GloVe: Global Vectors for Word Representation**

GloVe is a pre-trained word embedding model that can capture semantic meanings of words. It is an unsupervised learning algorithm developed by Stanford. Their disadvantage is that they are context-free and fail to capture higher-level concepts in context.

**Article: word2vec Explained: Deriving Mikolov et al.’s Negative-Sampling Word-Embedding Method**

Developed by Google, Word2Vec is another word embedding model that uses shallow neural network. It's not for deep learning.

## Pre-trained transformer language models

In recent years, the use of pre-trained language models has played a significant role in advancing natural language processing (NLP) tasks such as reading comprehension, text generation, and even creative writing **(Ke-Li add ref)**. Pre-trained models remove the need for researchers to prepare training datasets or allot computational resources to the stage of pre-training. Because of this, there has been substantial development in NLP research. OpenAI and Google are two companies that are considered pioneers in artificial intelligence and they both develop pre-trained models that are considered state-of-art; we will discuss the GPT models from OpenAI and the BERT model from Google.

### GPT

@@

OpenAI is an AI research company who openly pursues Artificial General Intelligence—to have machines learn and understand any intellectual tasks as human do **(Ke-Li add ref)**. OpenAI's Generative Pre-Trained Transformer (GPT) models are pre-trained language models that are built based on the transformer architecture. Proposed by @vaswani2017attention from Google in 2017, the Transformer is a novel network architecture that outperforms RNN-based models in computational efficiency and CNN-based in (something that it doesn't have to look for longer sentences) **(Keli add citation)**. [Write about self-attention layer and how it differentiate from RNN and CNN].

As of August 2020, OpenAI has three generations of GPT models. GPT was introduced to the public in June, 2018. In the year 2019, its successor GPT-2 was released in three stages. Not long after, in June 2020, OpenAI announced GPT-3, which is the latest GPT model as of July 2020 (@brown2020language). Since the API of GPT-3 at the moment is only available to a few invited users, public applications of GPT-3 are limited. On the other hand, its predecessor, GPT-2, has enabled researchers made breakthroughs in the past years. @alt2019fine extended GPT-2 to relation extraction, which is a task of identifying the relationship between concepts appeared in text. They had shown a milestone in predicting larger range of distinct relation types with higher confidence **(Ke-Li add ref)**. In the field of speech recognition, data scarcity is often an issue due to the difficulty to collect large amount of data from human for learning **(Ke-Li add ref)**. @bird2020lstm employed GPT-2 as part of the solution to generate augmented data for classification. GPT-2 also helped NLP researchers tackling the task of textual paraphrasing **(Ke-Li add ref)**. @hegde2020unsupervised used GPT-2 to build an unsupervised paraphrasing model that is not restricted by domain shift within an article, which is a problem faced by the usual supervised models of paraphrasing.

GPT-2 has the capacity to adapt to a context and generates custom output with the "fine-tuning" technique **(Ke-Li add ref)**. While the pre-training is unsupervised, fine-tuning is conducted by supervised learning or reinforced learning (@ziegler2019fine). **(Ke-Li add more about fine-tuning)** We aim to use GPT-2 to clean textual data to **(Ke-Li add more about how we use fine-tuning to train GPT-2 for text cleaning)**

GPT-3 has over 175 billions of parameters (@brown2020language). The parameters refer to the weights of the connections that enable the neural network to learn **(Keli add citation)**. In the past few years, the growth of parameters of transformer language models expands rapidly. The first generation GPT has 110 million parameters. Released in 2018, GPT-2 has 1.6 billion parameters, and within two years, GPT-3 has grown the size to 175 billion, which is over 100 times than its predecessor. The more parameters there are the better the model can generalize to new tasks; therefore, the increasing amount of parameters accelerates the improvements in text synthesis and downstream NLP tasks **(Keli add citation)**. GPT-3 can learn NLP tasks with just a handful of example; OpenAI refers this ability as few-shot learning, or in-context learning. **(Keli add citation)**. As a result, we only need to provide GPT-3 a few demonstrations for it to learn a new NLP task. For example, OpenAI team trained GPT-3 to generate "news articles". The prompt input is a plausible first sentence of a news story written by human, and the output is an entire news article generated by the model itself. Without the demonstrations, GPT-3 tends to treat the prompts as "tweets" and generate texts that serve as responses or follow-up tweets. The team fed a few previous news articles in the model’s context as demonstrations, and the model learned to produce the outputs that adapt to the style and length of news stories (@brown2020language). This few-shot learning ability indicates that the model can learn like human do and would democratize the use of language models to broader fields.

### BERT

**Article: Bert: Pre-training of deep bidirectional transformers for language understanding**

This paper is published by researchers at Google AI Language in 2018. The key innovation of BERT is its application of bidirectional training of the Transformer model, which results in a deeper sense of language context and flow.
